Estimation of Stochastic Wilson and Cowan Neural Field Model using Expectation Maximisation Algorithm

### 2011-08-20 ltx/data_paper/DataPaper.tex
minor correction to M step
correction to the computational complexity table

 \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&=-(T-1)n_y\ln \sigma_{\epsilon}^2-(T-1)n_x\ln\sigma_d^2\nonumber \\

@@

&-(T-1)n_y\ln \sigma_{\epsilon}^2-(T-1)n_x\ln\sigma_d^2-\frac{1}{\sigma_d^2}\mathrm{tr}\left\lbrace \boldsymbol\Xi_{0} \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace +\frac{2\xi}{\sigma_d^2} \mathrm{tr}\left\lbrace \boldsymbol\Xi_{1} \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace 

@@

 \frac{\partial \mathcal Q}{\partial\xi}=\frac{2}{\sigma_d^2}\mathrm{tr}\left\lbrace \boldsymbol\Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace -\frac{2\xi}{\sigma_d^2}\mathrm{tr}\left\lbrace \boldsymbol\Xi_2 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\frac{2}{\sigma_d^2}\boldsymbol\Xi_5,

@@

setting \eqref{eq:Qpartialxi} to zero and solving for $\xi$ gives

@@

  \frac{\partial \mathcal Q}{\partial \sigma_{\epsilon}^2}=-(T-1)n_y\frac{1}{\sigma_{\epsilon}^2}+\frac{1}{\sigma_{\epsilon}^4}\mathrm{tr}\left\lbrace\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace,

@@

 \hat{\sigma}_{\epsilon}^2=\frac{1}{(T-1)n_y}\sum_{t=0}^{T-1}\mathrm{tr}\left\lbrace (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top \right\rbrace.

@@

 \frac{\partial \mathcal Q}{\partial \sigma_d^2}&= -(T-1)n_x\frac{1}{\sigma_d^2}+\frac{1}{\sigma_d^4}\mathrm{tr}\left\lbrace \boldsymbol\Xi_0 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\frac{2\xi}{\sigma_d^4} \mathrm{tr}\left\lbrace \boldsymbol\Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace  \nonumber \\

@@

\hat{\sigma}_d^2&=\frac{1}{(T-1)n_x}\left[ \mathrm{tr}\left\lbrace \boldsymbol\Xi_0 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-

@@

 \frac{\partial \mathcal Q^2}{\partial^2\sigma_{\epsilon}^2}&\biggr\rvert_{\sigma_{\epsilon}=\hat{\sigma}_{\epsilon}}&&=-\frac{(T-1)n_y}{\hat{\sigma}_{\epsilon}^4} \label{eq:SecondDerivativenoise} \\
 \frac{\partial \mathcal Q^2}{\partial^2\sigma_{d}^2}&\biggr\rvert_{{\sigma}_{d}=\hat{\sigma}_{d}}&&= -\frac{(T-1)n_x}{\hat{\sigma}_{d}^4} \label{eq:SecondDerivativedisturbance}

@@

$\boldsymbol\Xi_3, \boldsymbol\Xi_5$&\eqref{eq:Xi3Ap},\eqref{eq:Xi5Ap} &$O(Tn_x^3)+O(Tn_x^2n_r)+O(Tn_xn_{\theta}n_r)$ \\

@@

\hat{\sigma}_{\epsilon}^2&=\frac{1}{(T-1)n_y}\sum_{t=0}^{T-1}\mathrm{tr}\left\lbrace (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top \right\rbrace \nonumber\\
\hat{\sigma}_d^2&=\frac{1}{(T-1)n_x}\left[ \mathrm{tr}\left\lbrace \boldsymbol\Xi_0 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-

>>>>

 \mathcal Q(\boldsymbol \Theta,\boldsymbol\Theta')&=-Tn_y\ln \sigma_{\epsilon}^2-Tn_x\ln\sigma_d^2\nonumber \\

@@

&-Tn_y\ln \sigma_{\epsilon}^2-Tn_x\ln\sigma_d^2-\frac{1}{\sigma_d^2}\mathrm{tr}\left\lbrace \boldsymbol\Xi_{0} \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace +\frac{2\xi}{\sigma_d^2} \mathrm{tr}\left\lbrace \boldsymbol\Xi_{1} \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace 

@@

 \frac{\partial \mathcal Q}{\partial\xi}=\frac{2}{\sigma_d^2}\mathrm{tr}\left\lbrace \boldsymbol\Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace -\frac{2\xi}{\sigma_d^2}\mathrm{tr}\left\lbrace \boldsymbol\Xi_2 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\frac{2}{\sigma_d^2}\boldsymbol\Xi_5\boldsymbol\theta,

@@

Substituting for $\boldsymbol\theta$ from \eqref{eq:thetahat} and then setting the result to zero and solving for $\xi$ gives

@@

  \frac{\partial \mathcal Q}{\partial \sigma_{\epsilon}^2}=-Tn_y\frac{1}{\sigma_{\epsilon}^2}+\frac{1}{\sigma_{\epsilon}^4}\mathrm{tr}\left\lbrace\sum_{t=0}^{T-1}\left[ (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top\right] \right\rbrace,

@@

 \hat{\sigma}_{\epsilon}^2=\frac{1}{Tn_y}\sum_{t=0}^{T-1}\mathrm{tr}\left\lbrace (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top \right\rbrace.

@@

 \frac{\partial \mathcal Q}{\partial \sigma_d^2}&= -Tn_x\frac{1}{\sigma_d^2}+\frac{1}{\sigma_d^4}\mathrm{tr}\left\lbrace \boldsymbol\Xi_0 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-\frac{2\xi}{\sigma_d^4} \mathrm{tr}\left\lbrace \boldsymbol\Xi_1 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace  \nonumber \\

@@

\hat{\sigma}_d^2&=\frac{1}{Tn_x}\left[ \mathrm{tr}\left\lbrace \boldsymbol\Xi_0 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-

@@

 \frac{\partial \mathcal Q^2}{\partial^2\sigma_{\epsilon}^2}&\biggr\rvert_{\sigma_{\epsilon}=\hat{\sigma}_{\epsilon}}&&=-\frac{Tn_y}{\hat{\sigma}_{\epsilon}^4} \label{eq:SecondDerivativenoise} \\
 \frac{\partial \mathcal Q^2}{\partial^2\sigma_{d}^2}&\biggr\rvert_{{\sigma}_{d}=\hat{\sigma}_{d}}&&= -\frac{Tn_x}{\hat{\sigma}_{d}^4} \label{eq:SecondDerivativedisturbance}

@@

$\boldsymbol\Xi_3, \boldsymbol\Xi_5$&\eqref{eq:Xi3Ap},\eqref{eq:Xi5Ap} &$O(Tn_x^2n_r)+O(Tn_xn_{\theta}n_r)$ \\

@@

\hat{\sigma}_{\epsilon}^2&=\frac{1}{Tn_y}\sum_{t=0}^{T-1}\mathrm{tr}\left\lbrace (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1}) (\mathbf y_{t+1}-\mathbf C\mathbf{\hat{x}}_{t+1})^\top+\mathbf C \mathbf P_{t+1}\mathbf C^\top \right\rbrace \nonumber\\
\hat{\sigma}_d^2&=\frac{1}{Tn_x}\left[ \mathrm{tr}\left\lbrace \boldsymbol\Xi_0 \tilde{\boldsymbol\Sigma}_e^{-1}\right\rbrace-
